Preferences interact: what consequences for a Schelling scenario?

### 2019-11-05 ethnic_value_rum.Rmd
add data

library(tidyverse)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(plyr)
library(foreach)

# data_eq_30_10 <- read.csv("50_g_30_bh_10bl.csv",sep = ",",skip = 6)      # eq_30 equal conditionn for high beta 30 beig recollected
#  names(data_eq_30_10) <- pull(read_csv("code_names.csv"))
#  data_eq_30_20 <- read.csv("50_g_30_bh_20bl.csv",sep = ",",skip = 6)
#   names(data_eq_30_20) <- pull(read_csv("code_names.csv"))
#  data_eq_30_30 <- read.csv("50_g_30_bh_30bl.csv",sep = ",",skip = 6)
#   names(data_eq_30_30) <- pull(read_csv("code_names.csv"))
#  raw_eq_30 <- rbind(data_eq_30_10,data_eq_30_20,data_eq_30_30)
#  write.csv(raw_eq_30, file = "eq_30.csv",row.names=FALSE)
# 
# 
# 
# eq_30 <- read.csv("eq_30.csv",sep = ",",skip = 6)
# names(eq_30) <- pull(read_csv("code_names.csv"))

eq_10 <- read.csv("50g_10_bh_10_bl.csv",sep = ",",skip = 6)
names(eq_10) <- pull(read_csv("code_names.csv"))

@@

@@

>>>>

library(tidyverse)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(plyr)
library(foreach)
library(dplyr)

eq_10 <- read.csv("50_g_10_bh.csv",sep = ",",skip = 6)
names(eq_10) <- pull(read_csv("code_names.csv"))

eq_30 <- read.csv("50_g_30_hb.csv", sep = ",", skip = 6)
names(eq_30) <- pull(read_csv("code_names.csv"))

@@

raw_f <- rbind(eq_30,eq_10,mj_30,mj_10)

df_e_sqr <- raw_f$e_sqr - raw_f$v_sqr
df_v_crl <-  raw_f$v_crl - raw_f$e_crl

dataset <- cbind(raw_f,df_e_sqr,df_v_crl)

# check <- final[,c(9,10,27,11,12,28)]

write.csv(dataset, file = "dataset.csv",row.names=FALSE) # later for reproduction

@@

```{r  heatmap, echo = FALSE}

dataset %>% filter(e_sqr == 30, v_crl == 30)
